Smoothing seismicity techniques applied to seismic sources characterization and probabilistic seismic hazard analysis in Brazil

### 2015-01-15 manuscript.tex
update some figures

%------------------------------------------------
\section{Brazilian seismicity data}

The main source of brazilian intraplate seismicity data is current the Brazilian Seismic Bulletin maintained mainly by the Seismological Certer, Institute of Astronomy, Geophysics and Atmospherical Sciences, University of São Paulo \citep{bsb_2014}. This catalog is a compilation from different sources.

@@

This catalog only cover crustal events. Andean deep subduction earthquakes with depht higher than 50km at west was discarded. This deep earthquakes contributions to the ground shaking hope to be consider in the future based on some new comprehensive south-american catalog.

@@

%------------------------------------------------
\section{Smoothing methods}
Under this work, three smoothing methods was considered. On this section brief explanation of each one will be done.

@@

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_seismicity_br}
	\caption{Brazilian earthquake catalog.}
	\label{fig_seismicity}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_hmtk_bsb2013_rate}
	\caption{Earthquake records by year}
	\label{fig_seismic_rate}
\end{figure}

@@

\begin{table}[H]
	\caption{BSB 2014.11 $M_W$ proxies \emph{ad-hoc} guidelines.}
	\begin{tabular}{l l l}
		\hline
		\textbf{magnitude source} & \textbf{rule} & \textbf{uncertainty}\\
		\hline
		% mb or equival & $$ M_W = 1.21m - 0.76 $$  & 0.3 \\
		% 		% magnitude from $A_f$  & $$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 8.4\times10^{-4}A_f^{1/2}& 0.4 \\
		$mb$ or $mR$ 
		&$ M_W(m) = 1.21 m - 0.76 $  
		& 0.3 \\
		Area felt $A_f$ 	
		&$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 0.00084\sqrt{A_f}$& 0.4 \\
		Maximum intensity $I_0$ 	
		& $mb(I_0) = 1.21 + 0.45 I_0$ then $M_W(m)$
		& 0.6 \\
		$mb$ and $A_f$ 	
		& $M_W(m, A_f) = 0.7 M_W(m) + 0.3 M_W(A_f)$
		& 0.33 \\
		\hline
	\end{tabular}
	\label{tab:guidelines}
\end{table}

>>>>

%------------------------------------------------
%
% seismicity data
% 
%------------------------------------------------

\section{Brazilian seismicity data}

Brazilian intraplate seismicity data is current the Brazilian Seismic Bulletin maintained mainly by the Seismological Certer, Institute of Astronomy, Geophysics and Atmospherical Sciences, University of São Paulo \citep{bsb_2014}. This catalog is a compilation from different sources.

@@

This catalog only cover crustal events. Andean deep subduction earthquakes with depht higher than 50km at west was discarded. This deep earthquakes contributions to the ground shaking hope to be consider in the future based on some new comprehensive south-american catalog. The epicenters on the catalog is shown on the figure \ref{fig_seismicity}.

@@

\subsection{Catalog overview}

Figure \ref{fig_overview} represent some parameters distribution on the catalog. Is easy to note that depth are not well defined into the catalog, and here all earthquakes will considered as in the shallow crust, around 15km.
From the figures \ref{fig_overview}a and \ref{fig_overview}b, is possible to note the behavior almost uniform on weekday distribution, and a slightly tendence to record earthquakes during the night. This could suggest some influence of daily noise level.

\subsection{Declustering procedures}

blsbalba

\subsection{Catalog completeness}

blsbalba

%------------------------------------------------
%
% smooothing methods
% 
%------------------------------------------------
\section{Smoothing methods}
Under this work, three smoothing methods was considered. On this section brief explanation of each one will be done.

@@

\begin{figure}
	\includegraphics[width=0.5\linewidth]{z_img_seismicity}
	\caption{Brazilian seismicity from 1767 to 2014. Source: \citep{bsb_2014}.}
	\label{fig_seismicity}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.20\textwidth} 
						 p{0.40\textwidth} 
						 p{0.40\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\				
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_depth}  &
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_weekday} &
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_hour}
		\end{tabular}
	\end{table}
	\caption{Catalogue overview. The histogram (a) shows the depth distribution. The histograms (b) and (c) represent the distributions of weekday and hour which earthquakes occur respectly. Dashed lines represent the mean value.}
	\label{fig_overview}
	\end{center}
\end{figure}

@@

@@

@@

\begin{table}[H]
	\caption{BSB 2014.11 $M_W$ proxies \emph{ad-hoc} guidelines.}
	\begin{tabular}{l l l}
		\hline
		\textbf{magnitude source} & \textbf{rule} & \textbf{uncertainty}\\
		\hline
		% mb or equival & $$ M_W = 1.21m - 0.76 $$  & 0.3 \\
		% 		% magnitude from $A_f$  & $$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 8.4\times10^{-4}A_f^{1/2}& 0.4 \\
		$mb$ or $mR$ 
		&$ M_W(m) = 1.121 m - 0.76 $  
		& 0.3 \\
		Area felt $A_f$ 	
		&$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 0.00084\sqrt{A_f}$& 0.4 \\
		Maximum intensity $I_0$ 	
		& $mb(I_0) = 1.21 + 0.45 I_0$ then $M_W(m)$
		& 0.6 \\
		$mb$ and $A_f$ 	
		& $M_W(m, A_f) = 0.7 M_W(m) + 0.3 M_W(A_f)$
		& 0.33 \\
		\hline
	\end{tabular}
	\label{tab:guidelines}
\end{table}
